Checkpoint 3

### 2020-04-23 Checkpoint3.Rmd
changes

Re-Cleaned 
```{r}
Finaldata <- Finaldata %>% select(-c(X)) 
Finaldata <- Finaldata %>% mutate(as.Date(Day))
```

@@

```{r}
## Creating a df of just the cases the week before 3/17
weekbefore <- data.frame(Finaldata) %>% filter(Day <= as.character(as.Date("2020-03-17")))

>>>>

Re-Cleaned 
```{r}
Finaldata <- Finaldata %>% select(-c(X)) 
Finaldata <- Finaldata %>% mutate(Day = as.Date(as.character(Day)))
```

@@

```{r}
## Creating a df of just the cases the week before 3/17
day1<-as.Date("2020-03-17")
weekbefore <- Finaldata %>% filter(Day <= day1)

Finaldata %>% 
  filter(Day <= day1)
